The socialization of meritocracy and market justice preferences at school

### 2024-07-04 07-supplementary-material.qmd
Update edit submit

---
author: "Equipo EDUMER"
format: pdf
editor: visual
---

## Appendix {#appendix}

@@

|                                                                                                                    |                                                                                                                                              |
|--------------------------------|---------------------------------------|
| **English translation**                                                                                            | **Original Spanish**                                                                                                                         |
| It is just that in Chile people who cna pay have a better education for their children                             | Es justo que en Chile las personas que puedan pagar tengan una mejor educación para sus hijos.                                               |
| It is just that in Chile people with higher incomes can have better pensions than people with low incomes          | Es justo que en Chile las personas con mayores ingresos puedan tener mejores pensiones que las personas de ingresos más bajos                |
| It is just that in Chile people with higher incomes can access better health services than people with low incomes | Es justo que en Chile las personas con mayores ingresos puedan acceder a una mejor atención de salud que las personas con ingresos más bajos |

>>>>

---
author: "Equipo EDUMER"
bibliography: "input/bib/just-ineq-merit.bib"
csl: "input/bib/apa6.csl"
---

## Supplementary Material {#appendix}

@@

|                                                                                                                    |                                                                                                                                              |
|---------------------------------|---------------------------------------|
| **English translation**                                                                                            | **Original Spanish**                                                                                                                         |
| It is just that in Chile people who cna pay have a better education for their children                             | Es justo que en Chile las personas que puedan pagar tengan una mejor educación para sus hijos.                                               |
| It is just that in Chile people with higher incomes can have better pensions than people with low incomes          | Es justo que en Chile las personas con mayores ingresos puedan tener mejores pensiones que las personas de ingresos más bajos                |
| It is just that in Chile people with higher incomes can access better health services than people with low incomes | Es justo que en Chile las personas con mayores ingresos puedan acceder a una mejor atención de salud que las personas con ingresos más bajos |

### 2024-07-04 paper.qmd
add quarto now extension
Update edit submit

---
format:
  html:
    keep-tex: true
editor: visual
bibliography: "input/bib/just-ineq-merit.bib"
csl: "input/bib/apa6.csl"
link-citations: true
mainfont: Times New Roman
---

# The socialization of meritocracy and market justice preferences at school

@@

{{< include 05-conclusiones.qmd >}}

{{< include 06-anexos.qmd >}}

>>>>

---
title: "The socialization of meritocracy and market justice preferences at school"
format:
  hikmah-pdf: 
    indent: false
  hikmah-manuscript-pdf: 
    indent: false
author:
  - name: Juan Carlos Castillo
    affiliations: Department of Sociology, Universidad de Chile
    email: juancastillov@uchile.cl
    attributes:
      corresponding: true
  - name: Mauricio Salgado
    affiliations: School of Sociology, Universidad Andrés Bello
  - name: Kevin Carrasco
    affiliations: Center for Social Conflict and Cohesion Studies
  - name: Andreas Laffert
    affiliations: Institute of Sociology, Universidad Católica de Chile
abstract: |
  This article evaluates novel approaches to do some really important things.
keywords: 
  - open-source 
  - scientific publishing
  - reproducible research
bibliography: "input/bib/just-ineq-merit.bib"
csl: "input/bib/apa6.csl"
link-citations: true
linestretch: 1.15       
mainfont: Times New Roman
fontsize: 12pt          
geometry: "left=2.54cm,right=2.54cm,top=2.54cm,bottom=2.54cm"
papersize: letter
colorlinks: true
fig-height: 4
fig-width: 7.5
header-includes:
  - \usepackage{threeparttable}
---

@@

{{< include 05-discussion.qmd >}}

{{< include 06-conclusion.qmd >}}
